Soss

### 2019-12-30 paper/paper.tex
unicode support
typo

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
\usepackage{jlcode}
\usepackage{todonotes}

@@

\begin{abstract}
We present Soss, a probabilistic programming language embedded in the Julia language. Soss represents statistical models in terms of abstract syntax trees, and uses staged compilation for on-demand generation of ``inference primitives'' (random sampling, log-density, etc) without reqquiring casual users to worry about such details.

>>>>

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
\usepackage{jlcode}
\usepackage{todonotes}
\usepackage{textalpha}

@@

\begin{abstract}
We present Soss, a probabilistic programming language embedded in the Julia language. Soss represents statistical models in terms of abstract syntax trees, and uses staged compilation for on-demand generation of ``inference primitives'' (random sampling, log-density, etc) without requiring casual users to worry about such details.
